Presentation

### 2017-02-14 paper_project2.Rmd
final commit with histogram

---
title: "Effectiveness of Therapy Treatment on Fibromyalgia"
author: "8532"
date: "2017-02-13"
header-includes:
    - \usepackage{setspace}\doublespacing
output: pdf_document
---

@@

```{r figure 1, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(long_pain, aes(x = pain)) + geom_density() + facet_wrap(condition ~
    time) + ggtitle("Figure 1: Density plots for pain by treatment and time point")
#ggplot(group_pain, aes(x = mean_pain)) + geom_density() + facet_wrap(condition ~ time) 
```

>>>>

---
title: "Effectiveness of Therapy Treatment on Fibromyalgia"
author: "8532"
date: "2017-02-14"
header-includes:
    - \usepackage{setspace}\doublespacing
output: pdf_document
---

@@

```{r figure 1, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(long_pain, aes(x = pain)) + geom_histogram() + facet_wrap(condition ~
    time) + ggtitle("Figure 1: Histograms for pain by treatment and time point")
#ggplot(group_pain, aes(x = mean_pain)) + geom_density() + facet_wrap(condition ~ time) 
```

### 2017-02-14 presentation.Rmd
final commit with histogram

---
title: "Presentation"
author: "Dylan Sun"
date: "2/13/2017"
output:
  slidy_presentation:
    font_adjustment: 2
---

@@

## Normality
- For the anovas
```{r figure 1, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(long_pain, aes(x = pain)) + geom_density() + facet_wrap(condition ~
    time) + ggtitle("Figure 1: Density plots for pain by treatment and time point")
#ggplot(group_pain, aes(x = mean_pain)) + geom_density() + facet_wrap(condition ~ time) 
```

>>>>

---
title: "Presentation"
author: "Dylan Sun"
date: "2017-02-14"
output: 
  slidy_presentation:
    font_adjustment: 2
---

@@

## Normality
- For the anovas
```{r figure 1, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(long_pain, aes(x = pain)) + geom_histogram() + facet_wrap(condition ~
    time) + ggtitle("Figure 1: Histograms for pain by treatment and time point")
#ggplot(group_pain, aes(x = mean_pain)) + geom_density() + facet_wrap(condition ~ time) 
```
